The Concurrent Calculi Formalisation Benchmark

### 2023-10-17 paper/paper.tex
reworded the HOAS and free variables comment

\subsubsection{Scope extrusion.}
This is the challenge most closely related to the POPLMark
challenge since it concerns the properties of binders in restrictions.
It is not clear that the techniques used to solve the original challenges about binders can be easily extended to reasoning about scope extrusion.
Notably, techniques like Higher Order Abstract Syntax, or well-scoped
De\ Bruijn indices do not have the concept of free variables. It is
not immediately obvious how to encode the operational semantics in
this kind of system.

>>>>

\subsubsection{Scope extrusion.}
This is the challenge most closely related to the POPLMark
challenge since it concerns the properties of binders in restrictions.
It is not clear that the techniques used to solve the original challenges about binders can be easily extended to reasoning about scope extrusion.
For example, techniques like Higher Order Abstract Syntax, or well-scoped
De\ Bruijn indices do not have the concept of free variables and thus encoding this challenge with them requires some attention.
